Outlier-preserving Focus and Context Visualization for Parallel Coordinates

### 2018-03-20 writeup/paper.tex
Cleanup
clean repo

To run the precomputing script on data.csv with 10 bins per axis, run \texttt{python3 bin.py data 10}. The input
data should have no quotes and end in \texttt{.csv}. This will also create array.png and array2.png. These show examples of the 
data before and after gaussian filtering.

@@

\section {System Differences}
Our implementation allows for the user to specify how many bins they want. The paper doesn't cover details of how the user interacts with their system, so we decided to simply add a command line argument to the precomputation script. This is accessible by running python3 bin.py n, where n is the number of bins desired per axis. 
Bradley talk about alpha blending here.

@@

\section {Case Study/Analysis Results}
\begin{tabular}{ |p{2cm}||p{1cm}||p{1cm}||p{1.2cm}|  }
 \hline
 \multicolumn{4}{|c|}{Time in Sec.} \\
 \hline
 Data& Orig. Time& Our Time & Rows\\
 \hline
 creditdefault& 13 & 8 & 10001\\
 quakes&   3 & 10 & 1001\\
 census &- &32min & 3058281\\
 EuStock &3.1 &8 & 1861\\
 age-alc &<1 &<1 & 396\\
 \hline
\end{tabular}

>>>>

To run the precomputing script on data.csv with 10 bins per axis, run \texttt{python3.6 bin.py data 10}. The input
data should have no quotes and end in \texttt{.csv}. We require python3.6 for matplotlib, which is needed
for gaussian filtering. This will also create array.png and array2.png. These show examples of the 
data before and after gaussian filtering. Alternatively, there are pre-created output.json files by us in /src/precomputed-data. 
Move those into /src and rename to ``output.json'' to try each out.

@@

\section {System Differences}
Our implementation allows for the user to specify how many bins they want. The paper doesn't cover details of how the user interacts with their system, so we decided to simply add a command line argument to the precomputation script. This is accessible by running python3 bin.py n, where n is the number of bins desired per axis.

@@

\section {Case Study/Analysis Results}
\begin{tabular}{ |p{2cm}||p{1cm}||p{1cm}||p{1.2cm}|  }
 \hline
 \multicolumn{4}{|c|}{Time in Sec.} \\
 \hline
 Data& Orig. Time& Our Time & Rows\\
 \hline
 creditdefault& 13 & 8 & 10001\\
 quakes&   3 & 10 & 1001\\
 census &- &32min & 3058281\\
 EuStock &3.1 &8 & 1861\\
 age-alc &$<1$ &$<1$ & 396\\
 \hline
\end{tabular}
